### 2022-04-08 spanish/sections/papers.tex
Update papers.tex

\item{Orchard, X., \& González-Bustamante, B. ({\itshape próximamente}). Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019). {\itshape The International Journal of Press/Politics}.}

@@

\begin{benumerate}{10}

@@

>>>>

\item{Orchard, X., \& González-Bustamante, B. (2022). Power Hierarchies and Visibility in the News: Exploring Determinants of Politicians’ Presence and Prominence in the Chilean Press (1991-2019). {\itshape The International Journal of Press/Politics}. Online First. {\scshape doi:} \href{https://doi.org/10.1177/19401612221089482}{\textcolor{blue}{10.1177/19401612221089482}}}

@@

\begin{benumerate}{12}

@@

\item{\small Gonz\'alez-Bustamante, B. (2021). Sofisticación, participación y compromiso político en América Latina. {\itshape Tufte Working Papers}, 2, 1--21. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. (2020). Aplicación de ForceAtlas2, un algoritmo de diseño gráfico continúo, para el estudio de las élites. {\itshape Tufte Working Papers}, 1, 1--15. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}}\vspace{1mm}
